---
title: "Syllabic affiliation of glides in chicano"
date: "Last update: `r Sys.Date()`"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Syllabic affiliation of glides in chicano

## Last update: `r Sys.Date()`

1. [data](./data/)
2. [praatScripts](./praatScripts/)
3. [rScripts](./rScripts/)
4. [sources](./sources/)

----

# Analyses

```{r, 'source_scripts', message=FALSE, warning=FALSE}
source("./rScripts/04_exploratory_plots.R")
```

## Syllabification task

The following plots show results from the syllabification task. Four syllable 
nonse words containing a CGVGC sequence in the penultimate syllable were 
presented on a screen. Participants read the words out loud, syllable by 
syllable. The plots show the overall distribution of the responses, which 
have been classified in the following manner: 

- **tripthong**: the critical sequence was produced in a single syllable 
- **vowel + dipthong**: the critical sequence was produced as two syllables: 
CV + VGC (labeled as 'hiatus'), e.g. "lakapiaisto" [la.ka.**pi**.'**ai̯s**.to]
- **simplification**: a segment was elided from the critical sequence, 
simplifying the critical syllable. The most common strategy was to drop the 
pre-vocalic glide, creating a sequence like [la.ka.**pai̯s**.to] instead of 
[la.ka.'**pjai̯s**.to]), but the post-vocalic glide was also dropped
occasionally. 

Figure 1 plots the proportion of responses accross all data (collapsing across 
the pre-vocalic glide and onset). We observe that tripthongs were produced 
in approximately 45% of the targets. A production containing a hiatus made up 
roughly 30% of the data, followed by a simplification of some sort (~25% of the 
time). 

```{r, 'hls_syllabification_p1', fig.retina=2, fig.align='center', fig.cap='hi'}
hls_syllabification_p1
```

```{r, 'hls_syllabification_p2', fig.retina=2, fig.align='center'}
hls_syllabification_p2
```

## Carrier sentence task

```{r, 'hls_carrier_dur_p1', fig.retina=2, fig.align='center'}
hls_carrier_dur_p1
```

```{r, 'hls_carrier_f1_p2', fig.retina=2, fig.align='center'}
hls_carrier_f1_p2
```

```{r, 'hls_carrier_int_p3', fig.retina=2, fig.align='center'}
hls_carrier_int_p3
```

```{r, 'hls_carrier_scatter_p4', fig.retina=2, fig.align='center'}
hls_carrier_scatter_p4
```

