---
title: "Syllabic affiliation of glides in chicano"
date: "Last update: `r Sys.Date()`"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Syllabic affiliation of glides in chicano

## Last update: `r Sys.Date()`

1. [data](./data/)
2. [praatScripts](./praatScripts/)
3. [rScripts](./rScripts/)
4. [sources](./sources/)

----

# Analyses

```{r, 'source_scripts', message=FALSE, warning=FALSE}
source("./rScripts/04_exploratory_plots.R")
```

## Syllabification task

The following plots show 4 syllable nonse words containing a CGVGC sequence as 
the penultimate syllable. The plots show the overall distribution of the 
responses, which were tripthong, vowel + dipthong (labelled as 'hiatus'), or 
a simplification of some sort (typically the pre-vocalic glide was dropped, 
creating a sequence like [pajs] instead of [pjajs])


```{r, 'hls_syllabification_p1', fig.retina=2}
hls_syllabification_p1
```

```{r, 'hls_syllabification_p2', fig.retina=2}
hls_syllabification_p2
```

## Carrier sentence task

```{r, 'hls_carrier_dur_p1', fig.retina=2}
hls_carrier_dur_p1
```

```{r, 'hls_carrier_f1_p2', fig.retina=2}
hls_carrier_f1_p2
```

```{r, 'hls_carrier_int_p3', fig.retina=2}
hls_carrier_int_p3
```

```{r, 'hls_carrier_scatter_p4', fig.retina=2}
hls_carrier_scatter_p4
```

