---
title: "Syllabic affiliation of glides in chicano"
date: "Last update: `r Sys.Date()`"
output: md_document
---

```{r 'setup', include=FALSE}
knitr::opts_chunk$set(echo=FALSE, fig.retina=2)
```

# Syllabic affiliation of glides in chicano

## Last update: `r Sys.Date()`

1. [data](./data/)
2. [praatScripts](./praatScripts/)
3. [rScripts](./rScripts/)
4. [sources](./sources/)

----

# Analyses

```{r, 'source_scripts', message=FALSE, warning=FALSE}
source("./rScripts/04_exploratory_plots.R")
```

## Syllabification task

The following plots show results from the syllabification task. Four syllable 
nonse words containing a CGVGC sequence in the penultimate syllable were 
presented on a screen. Participants read the words out loud, syllable by 
syllable. The plots show the overall distribution of the responses, which 
have been classified in the following manner: 

- **tripthong**: the critical sequence was produced in a single syllable 
- **vowel + dipthong**: the critical sequence was produced as two syllables: 
CV + VGC (labeled as 'hiatus'), e.g. "lakapiaisto" [la.ka.**pi**.'**ai̯s**.to]
- **simplification**: a segment was elided from the critical sequence, 
simplifying the critical syllable. The most common strategy was to drop the 
pre-vocalic glide, creating a sequence like [la.ka.**pai̯s**.to] instead of 
[la.ka.'**pjai̯s**.to]), but the post-vocalic glide was also dropped
occasionally. 

Figure 1 plots the proportion of responses across all data (collapsing across 
the pre-vocalic glide and onset). We observe that tripthongs were produced 
in approximately 45% of the targets. A production containing a hiatus made up 
roughly 30% of the data, followed by a simplification of some sort (~25% of the 
time). 

```{r, 'hls_syllabification_p1', fig.cap='Figure 1: Responses in syllabification task.'}
hls_syllabification_p1
```

If we combine `hiatus` and `simplification` (Figure 2), we see that they make 
up approximately 60% of the data. 

```{r, 'hls_syllabification_p2', fig.cap="Figure 2: Responses in syllabification task combining 'hiatus/simplification'."}
hls_syllabification_p2
```

Overall, the task provides evidence supporting the hypothesis that pre-vocalic 
glides can be part of the onset in this variety of Spanish. 

**To consider**: 

- What factors can explain the variation in response types?
- Possibilities: 
    - Frontness of glide. Is there a difference between [j] and [w]?
    - Preceding consonant. The pre-vocalic glides in this task are preceded 
    by a stop (voiced and voiceless) or [f]. Is there is a difference in 
    response strategies as a function of preceding consonant?
- Figure 3 suggests that frontness and preceding consonant are not critical in 
determining response type. 

```{r, 'hls_syllabification_all_p3', fig.cap="Figure 3: Responses in syllabification task as a function of glide, preceding consonant, and voicing."}
hls_syllabification_all_p3
```

**Statistical analysis**: 

- Multinomial mixed effects regression 
- Criterion: response (tripthong/hiatus/simplification)
- Predictors: glide ([j]/[w]), consonant ([b, d, g, p, t, k, f])
- Random effects: 
    - `(1 + glide + consonant | participant)`
    - `(1 + glide + consonant | item)`
- Another possibility is to combine hiatus/simplification and use standard 
logistic regression. 


</br></br></br>

## Carrier sentence task

The following plots illustrate the results from the carrier sentence task. These 
analyses test the hypothesis that pre-vocalic glides will be disallowed if 
preceded by a palatal consonant. To test this, we measure duration, F1, and 
intensity of the pre-vocalic glide in two environments: after a palatal 
consonant and after any other consonant. If pre-vocalic glides are blocked 
after palatals, we expect to observe differences in overall duration. Figure 3 
plots the duration data. 

```{r, 'hls_carrier_dur_p1', fig.cap="Figure 3: Duration as a function of preceding consonant."}
hls_carrier_dur_p1
```

We see a longer duration for glide segments following a palatal consonant 
(contrary to the hypothesis). There are two possible explanations (that I can 
think of). 1) The participants are able to produce a glide in this context (at 
least in some cases) because the preceding consonant is not palatal (i.e., 'ch' 
is surfacing as [ʃ] or the fact that it is alveo-palatal is different enough to 
allow a glide afterwards). 2) The participants are not producing a glide, but 
rather are lengthening the onset. 

We can examine the plausibility of (1) by looking at the formant trajectory over 
the course of the segment. If the participants are able to produce a glide in 
some contexts but not others we should see differences in F1 as a function of 
the preceding consonant. 

![gam-f1]("figs/plot_phrase_tc_f1.pdf")

Again, the second possibility is that participants are lengthening the palatal 
consonant (not producing a glide) because of the fact that they cannot produce 
both. In other words, they might be trying to produce something, but because 
the target is illicit, they resort to lengthening the onset. If this is indeed 
what is happening, then we would expect the intensity of the lengthened segment 
to be lower from that of a glide. Why? Because more consonant-like productions 
have lower intensity than more vowel-like productions. Thus we analyze the time 
course of intensity in order to see how the two environments differ as they 
near the following [a].

![gam-int](figs/plot_phrase_tc_int.pdf)

![gam-int-dif](figs/plot_phrase_tc_diff_int.pdf)
