---
title: "Syllabic affiliation of glides in chicano"
date: "Last update: `r Sys.Date()`"
output: md_document
---

```{r 'setup', include=FALSE}
knitr::opts_chunk$set(echo=FALSE, fig.retina=2, fig.align='center')
```

# Syllabic affiliation of glides in chicano

## Last update: `r Sys.Date()`

1. [data](./data/)
2. [praatScripts](./praatScripts/)
3. [rScripts](./rScripts/)
4. [sources](./sources/)

----

# Analyses

```{r, 'source_scripts', message=FALSE, warning=FALSE}
source("./rScripts/04_exploratory_plots.R")
```

## Syllabification task

The following plots show results from the syllabification task. Four syllable 
nonse words containing a CGVGC sequence in the penultimate syllable were 
presented on a screen. Participants read the words out loud, syllable by 
syllable. The plots show the overall distribution of the responses, which 
have been classified in the following manner: 

- **tripthong**: the critical sequence was produced in a single syllable 
- **vowel + dipthong**: the critical sequence was produced as two syllables: 
CV + VGC (labeled as 'hiatus'), e.g. "lakapiaisto" [la.ka.**pi**.'**ai̯s**.to]
- **simplification**: a segment was elided from the critical sequence, 
simplifying the critical syllable. The most common strategy was to drop the 
pre-vocalic glide, creating a sequence like [la.ka.**pai̯s**.to] instead of 
[la.ka.'**pjai̯s**.to]), but the post-vocalic glide was also dropped
occasionally. 

Figure 1 plots the proportion of responses accross all data (collapsing across 
the pre-vocalic glide and onset). We observe that tripthongs were produced 
in approximately 45% of the targets. A production containing a hiatus made up 
roughly 30% of the data, followed by a simplification of some sort (~25% of the 
time). 

```{r, 'hls_syllabification_p1', fig.cap='Figure 1: Responses in syllabification task.'}
hls_syllabification_p1
```

If we combine `hiatus` and `simplification` (Figure 2), we see that they make 
up approximately 60% of the data. 

```{r, 'hls_syllabification_p2', fig.cap="Figure 2: Responses in syllabification task combining 'hiatus/simplification'"}
hls_syllabification_p2
```

Overall, the task provides evidence supporting the hypothesis that pre-vocalic 
glides can be part of the onset in this variety of Spanish. 

**To consider**: 

- What factors can explain the variation in response types?
- Possibilities: 
    - Frontness of glide. Is there a difference between [j] and [w]?
    - Preceeding consonant. The pre-vocalic glides in this task are preceeded 
    by a stop (voiced and voiceless) or [f]. Is there is a difference in 
    response strategies as a function of preceeding consonant?

**Statistical analysis**: 

- Multinomial mixed effects regression 
- Criterion: response (tripthong/hiatus/simplification)
- Predictors: glide ([j]/[w]), consonant ([b, d, g, p, t, k, f])
- Random effects: 
(1 + glide + consonant | participant) + (1 + glide + consonant | item)
- Another possibility is to combine hiatus/simplification and use standard 
logistic regression. 



## Carrier sentence task

```{r, 'hls_carrier_dur_p1'}
hls_carrier_dur_p1
```

```{r, 'hls_carrier_f1_p2'}
hls_carrier_f1_p2
```

```{r, 'hls_carrier_int_p3'}
hls_carrier_int_p3
```

```{r, 'hls_carrier_scatter_p4'}
hls_carrier_scatter_p4
```

