## Bayesian Data Analysis

The present work uses Bayesian Data Analysis (BDA) for statistical inferences. 
This implies that we do not focus on a single point estimate for a given parameter &beta;, but rather we use Bayes Theorem to derive a posterior distribution of plausible estimates of &beta;. 
Importantly, we do not use p-values or any other decision rules for determining the importance of an effect. 
BDA allows us to quantify our uncertainty in a more straightforward way with regard to our statistical models and focus on estimation.

## Syllable division task

The first model analyzed the syllabification task data using multinomial logistic regression. 
The participants responses (triphthong, hiatus, simplification) were modeled in a simple, intecept-only model, and as a function of the post-consonantal glide ([j], [w]). 
Table \@ref(tab:syllabification-all-models-table) below provides the complete output summary of the model.

```{r, syllabification-all-models-table}
tab_multi_all %>% 
  knitr::kable(
    format = "pandoc", align = c("l", "l", "r", "r", "r", "r", "r"), 
    caption = "Model summary for the syllabification task. The table reports 
    posterior medians, 95\\% credible intervals, and probability of direction 
    to assess estimates, along with Rhat and Effective sample size to assess 
    model fit.",
    label = "syllabification-all-models-table")

```


## Phrase reading task

### GAMMs

GAMMs represent an extension to the linear model framework that allow non-linear functions called factor smooths to be applied to predictors. 
In this sense, the predictors can be classified into two types: parametric terms (equivalent to fixed effects in hierarchical model terminology) and smooth terms. 
Random smooths are conceptually similar to random slopes and intercepts in the mixed-effects regression framework [@winter2016].
Thus, they allow the by-subject trajectory shapes to vary as a function of a parametric effect and are essential in avoiding anti-conservative models.

### F1

The model summary output of the duration model is available in Table \@ref(tab:carrier-dur) here: 

```{r, carrier-dur}
tab_dur %>% 
  knitr::kable(
    format = "pandoc", align = c("l", "r", "r", "r", "r", "r"), 
    caption = "Model summary for the duration analysis. The table reports 
    posterior medians, 95\\% credible intervals, and probability of direction 
    to assess estimates, along with Rhat and Effective sample size to assess 
    model fit.",
    label = "carrier-dur")
```


The full model specification used to fit the F1 GAMM is provided below, followed by the full output of the model summary in Table \@ref(tab:carrier-f1-gam). 

```r
# Set priors
priors <- c(
  prior(normal(0, 0.5), class = Intercept), 
  prior(normal(0, 0.5), class = b), 
  prior(
    student_t(3, 0, 1), 
    class = sds, 
    coef = s(time_course_segment, bs = "cr", k = 3)), 
  prior(
    student_t(3, 0, 2.5), 
    class = sds, 
    coef = s(time_course_segment, by = is_palatal_ord, bs = "cr", k = 4)), 
  prior(
    student_t(3, 0, 2.5), 
    class = sds, 
    coef = s(time_course_segment, participant, bs = "fs", m = 1, k = 3)), 
  prior(cauchy(0, 2), class = sigma)
  )

# Model formula
mode_formula <- bf(
 f1norm ~ is_palatal_ord + 
  s(time_course_segment, bs = "cr", k = 3) + # ref smooth
  s(time_course_segment, by = is_palatal_ord, bs = "cr", k = 4) + # diff
  s(time_course_segment, participant, bs = "fs", m = 1, k = 3), # random 
)

# F1 GAM
b_gam_f1 <- brm(
  formula = model_formula
  family = gaussian(), 
  prior = priors, 
  backend = "cmdstanr", iter = 2000, warmup = 1000, cores = 4,
  control = list(adapt_delta = 0.999999, max_treedepth = 20), 
  data = carrier_tc_final_gamm, 
  )
```


```{r, carrier-f1-gam}
tab_gam_f1 %>% 
  knitr::kable(
    format = "pandoc", align = c("l", "l", "r", "r", "r", "r", "r"), 
    caption = "Model summary for the F1 GAMM. The table reports 
    posterior medians, 95\\% credible intervals, and probability of direction 
    to assess estimates, along with Rhat and Effective sample size to assess 
    model fit.",
    label = "carrier-f1-gam")
```

An exploratory model not reported on the time course of the intensity measurements is provided below in Table \@ref(tab:carrier-int-gam). 

```{r, carrier-int-gam}
tab_gam_int %>% 
  knitr::kable(
    format = "pandoc", align = c("l", "l", "r", "r", "r", "r", "r"), 
    caption = "Model summary for the F1 GAMM. The table reports 
    posterior medians, 95\\% credible intervals, and probability of direction 
    to assess estimates, along with Rhat and Effective sample size to assess 
    model fit.",
    label = "carrier-int-gam")
```


## Reproducibility information

**About this document**  

This document was written in RMarkdown using `papaja` [@R-papaja].  

**Session info**  

```{r, session-info, comment=""}
devtools::session_info()$platform
as.data.frame(devtools::package_info())[, c(3, 8)]
```
