## Bayesian Data Analysis

In all cases we used Bayesian Data Analysis (BDA, CITE) for statistical inferences. 


## Syllabification task

The first model analyzed the syllabification task data using multinomial logistic regression. 
The participants responses (triphthong, hiatus, simplification) were modeled in a simple, intecept-only model, and as a function of the post-consonantal glide ([j], [w]). 

Table \@ref(tab:syllabification-all-models-table) below.

```{r, syllabification-all-models-table}
tab_multi_all %>% 
  knitr::kable(
    format = "pandoc", align = c("l", "l", "r", "r", "r", "r", "r"), 
    caption = "Model summary for the syllabification task. The table reports 
    posterior medians, 95\\% credible intervals, and probability of direction 
    to assess estimates, along with Rhat and Effective sample size to assess 
    model fit.",
    label = "syllabification-all-models-table")

```


## Carrier task

### GAMMs

GAMMs represent an extension to the linear model framework that allow non-linear functions called factor smooths to be applied to predictors. In this sense, the predictors can be classified into two types: parametric terms (equivalent to fixed effects in hierarchical model terminology) and smooth terms. 
Random smooths are conceptually similar to random slopes and intercepts in the mixed-effects regression framework [@winter2016].
Thus, they allow the by-subject trajectory shapes to vary as a function of a parametric effect and are essential in avoiding anti-conservative models.

### F1

Table \@ref(tab:carrier-dur) below.

```{r, carrier-dur}
tab_dur %>% 
  knitr::kable(
    format = "pandoc", align = c("l", "r", "r", "r", "r", "r"), 
    caption = "Model summary for the duration analysis. The table reports 
    posterior medians, 95\\% credible intervals, and probability of direction 
    to assess estimates, along with Rhat and Effective sample size to assess 
    model fit.",
    label = "carrier-dur")
```

Table \@ref(tab:carrier-f1-gam) below.

```{r, carrier-f1-gam}
tab_gam_f1 %>% 
  knitr::kable(
    format = "pandoc", align = c("l", "l", "r", "r", "r", "r", "r"), 
    caption = "Model summary for the F1 GAMM. The table reports 
    posterior medians, 95\\% credible intervals, and probability of direction 
    to assess estimates, along with Rhat and Effective sample size to assess 
    model fit.",
    label = "carrier-f1-gam")
```

Table \@ref(tab:carrier-int-gam) below.

```{r, carrier-int-gam}
tab_gam_int %>% 
  knitr::kable(
    format = "pandoc", align = c("l", "l", "r", "r", "r", "r", "r"), 
    caption = "Model summary for the F1 GAMM. The table reports 
    posterior medians, 95\\% credible intervals, and probability of direction 
    to assess estimates, along with Rhat and Effective sample size to assess 
    model fit.",
    label = "carrier-int-gam")
```



